Moral Foundations of U.S. Political News Organizations

### 2019-03-25 pilot_manuscript.Rmd
rush time

````{r Rush Limbaugh, eval = F, include = F}
url8 = 'https://www.rushlimbaugh.com/?s=kavanaugh&is_v=1'
webpage8 = read_html(url8)
#headline_data8 = html_nodes(webpage8, 'a')    trying something different
headline_data8 = html_nodes(webpage8, '.ais-hits--content a')

attr_data8 = html_attrs(headline_data8) 
attr_data8

urlslist8 = unlist(attr_data8)
urlslist8 = urlslist8[grep(urlslist8)]

##start a data frame
RushDF = matrix(NA, nrow = length(urlslist8), ncol = 3)
colnames(RushDF) = c("Source", "Url", "Text")
RushDF = as.data.frame(RushDF)

##for loops
for (i in 1:length(urlslist8)){

  ##read in the URL
  webpage8 <- read_html(urlslist8[i])

  ##pull the specific nodes
  headline_data8 = html_nodes(webpage8,'p')

  ##pull the text
  text_data8 = html_text(headline_data8)

  ##save the data
  RushDF$Source[i] = "Rush Limbaugh"
  RushDF$Url[i] = urlslist8[i]
  RushDF$Text[i] = paste(text_data8, collapse = "")
} ##end for loop
```

>>>>

```{r Breitbart_gs, eval = F, include = F}
library(rvest)
library(RSelenium)
library(beepr)
library(lubridate)

url = "https://www.breitbart.com/tag/government-shutdown/"

#loop over the results and go through them
for (i in 1:16){

  if (i > 1)
    {
  url = paste0("https://www.breitbart.com/tag/government-shutdown/page/",
               i+1, "/")
  remDr$navigate(url)
  }

#pull only the right dates
rows = rownames(temp2[ (temp2$`5` == 2018 | temp2$`5` == 2019) & #must be 2018/19 and  
                         (
                           (temp2$`6` == "12" & as.numeric(temp2$`7`)>8 & temp2$`5` == 2018) | #after dec 12
                             (temp2$`6`== "01" & temp2$`5` == 2019) | #all of jan
                             (temp2$`6` == "02" & as.numeric(temp2$`7`)<8 & temp2$`5` == 2019)
                         ), #before feb 8
                       ])

write.csv(BREITBARTDF, "BREITBART_gs.csv", row.names = F)
```

````{r Rush_kav, eval = F, include = F}
library(rvest)
library(RSelenium)
library(beepr)
library(lubridate)

url = "https://www.rushlimbaugh.com/?s=kavanaugh&is_v=1"

#loop over the results and go through them
##18 pages
for (i in 1:18){

  #find the urls for page X
  webElems <- remDr$findElements(using = "css", "a")

  #find the thing to click on 
  webClick <- remDr$findElements(using = "css", ".ais-pagination--link")

  #click on the page number
  webClick[[18]]$clickElement()

##deal with the URLS
urlslist = unlist(urlslist_final)
urlslist = unique(urlslist)
urlslist = urlslist[-c(grep("store", urlslist))] #take out store
urlslist = urlslist[grep("/daily/[0-9]*/[0-9]*/[0-9]*/[a-zA-Z]", urlslist)]

##start a data frame
RUSHDF = matrix(NA, nrow = length(urlslist3), ncol = 3)
colnames(RUSHDF) = c("Source", "Url", "Text")
RUSHDF = as.data.frame(RUSHDF)

for (i in 49:length(urlslist3)){

  ##save the data
  RUSHDF$Source[i] = "RUSH"
  RUSHDF$Url[i] = urlslist3[i]
  RUSHDF$Text[i] = paste(text_data2, collapse = "")

write.csv(RUSHDF, "RUSH_kav.csv", row.names = F)
```
